Do More Subdivisions in Wards Increase Turnout? An Analysis of the 2022 Toronto Municipal Election

### 2023-06-02 outputs/paper/paper.qmd
changes to graph

head(summarized_voter_statistics, 25) |>
  kable(
    col.names = c("Ward", "Number of Subdivisions"), 
    booktabs = TRUE
  )
```

@@

#code referenced from: https://github.com/christina-wei/INF3104-1-Covid-Clinics/blob/main/outputs/paper/covid_clinics.qmd
cleaned_voter_statistics |>
  ggplot(aes(x = ward), "-", sub, fill = location_type) + 
  geom_bar() + #bar graph
  theme_minimal() + #neater theme
  theme(axis.text.x = element_text(angle=90, size = 6)) + #rotate x-axis & smaller font
  labs(
    title = "Number of Subdivisions Per Ward in Toronto",
    x = "Ward",
    y = "Number of Subdivisions",
    fill = "Type"
  )  #a

>>>>

summarized_voter_statistics |>
  kable(
    col.names = c("Ward", "Number of Subdivisions"), 
    booktabs = TRUE
  )
```

@@

#code referenced from: https://github.com/christina-wei/INF3104-1-Covid-Clinics/blob/main/outputs/paper/covid_clinics.qmd
summarized_voter_statistics |>
  ggplot(aes(x = ward), "-", sub, fill = n) + 
  geom_bar() + #bar graph
  theme_minimal() + #neater theme
  theme(axis.text.x = element_text(angle=90, size = 6)) + #rotate x-axis & smaller font
  labs(
    title = "Number of Subdivisions Per Ward in Toronto",
    x = "Ward",
    y = "Number of Subdivisions",
    fill = "Type"
  )  #a
